%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[margin, centered]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
\newsectionwidth{1in}
\usepackage[pdftex]{graphicx}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{helvet}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------\
\begin{center}
    \hspace{-\hoffset}
    \huge\bf{{SANTOSH G}}
\end{center}
\vspace{-7mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}
\vspace{-9mm}
\begin{center}
    \hspace{-\hoffset}
    \href{mailto:santoshgunashekar@gmail.com}{santoshgunashekar@gmail.com} ~\textbullet~ \(+91\) 8197421851 ~\textbullet~ \ Bengaluru, India ~\textbullet~ \href{https://www.linkedin.com/in/santosh-g-163ab3106}{linkedin : Santosh Gunashekar}
\end{center}
\vspace{-7mm}
\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{B.Tech in Computer Science and Engineering } \hfill 2016 - 2020 \\
\textnormal{Ramaiah University of Applied Sciences, Bengaluru, India}
\begin{itemize}
 \item Aggregate of 8.1/10 at the end of 4th Semester
\end{itemize}
\textbf{High School} : {PUC in Computer Science} \hfill 2014 - 2016 \\
\textnormal{Shri Bhagawan Mahaveer Jain College, Bengaluru, India}
\begin{itemize}
 \item Secured 92.5\%
\end{itemize}
\textbf{Secondary School :}\textnormal{ St. Mira's High School, Bengaluru, India} \hfill 2002 - 2014
\begin{itemize}
 \item Secured 90.33\% in ICSE
\end{itemize}
%----------------------------------------------------------------------------------------
%
%---------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%---------------------------------------------------------------------------------------
%
\section{Experience}
\begin{itemize}[leftmargin=*]
\item  \textbf{Machine Learning Intern},\hfill June 2018 - July 2018
\newline \textnormal{Internity Foundation, Uttar Pradesh, India}  
\end{itemize} 
%
%
%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Technical \hspace{2mm} Skills}
\textbf{Languages} - Java, C, C++, Python, HTML, SQL, Haskell, x86 (Assembly Language). \\
\textbf{Software Tools/Packages} - Matlab, Android, MySQL, NetBeans\\
\textbf{Platforms} - Linux and Windows
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	RELEVANT COURSE SECTION
%----------------------------------------------------------------------------------------
\section{Relevant \hspace{2mm} Courses}
\begin{itemize}[leftmargin=*]
\item  \textbf{Computer Science}: Data Structures and Algorithms, Discrete Mathematics, Computer Organisation and 
Architecture, Design and Analysis of Algorithms, Formal Languages and Automata Theory, Software
Engineering, Programming Language Principles, Simulation, Operating System
\item  \textbf{Mathematics}: Machine Learning (Online course in Coursera), Linear Algebra,
Differential Equations.
\end{itemize}
%----------------------------------------------------------------------------------------

%	Selected Projects Section
%----------------------------------------------------------------------------------------
\section{Projects and Hackathons}
All projects available on git : \href{https://github.com/santoshguna001}{ github.com/santoshguna001 }
\begin{itemize}[leftmargin=*]
\item  \textbf{Permutations and Combinations}: Built a mobile application which finds the permutations and
combinations of the input string, and selectively shows meaningful
words.
\item  \textbf{Innovate India, Texas Instrumentals(TI) 2017}: Built a smart water billing system using
the IoT tools made available by the TI only. 
\item  \textbf{CMRIT Hacks 24Hr 2018}: Built a mobile application Teleport to encounter tourism issues and provide
a good platform to search for tourist attractions, book hotels, transport, et cetera. 
\item  \textbf{NAPEM 2018}: Presented the concept of identifying the seizures during the onset phase in medical hackathon-workshop with the
insight of a paediatrician, a  team including students from medical electronics.
\item \textbf{Content Filtering} : Developed a machine learning model to remove abusive content in text, images and audio. The model beeps the abusive words, abusive images are blurred and abusive text removed.
\item \textbf{Hackit-on 2.0, 2018} : Developed an application to solve generic problems faced in urban centres using realtime database, deeplink UPI, firebase storage.
\begin{itemize}
 \item \textbf{Hackman, 2018} : Improvements on the application
\end{itemize}
\item \textbf{Dexterix, 2018} : Worked on dynamic ad generation based on local trending searches using twitter data.
\end{itemize}



%	ACHIEVEMENT SECTION
%----------------------------------------------------------------------------------------

\section{Achievements and Awards}
\begin{itemize}[leftmargin=*]
 \item Received the \textbf{Best} intern award in Machine Learning, July 2018
 \item Bagged \textbf{Second} prize in Programming Skills intercollegiate competition, 2015.
 \item LEOS-ISRO Quiz 2018: Bagged \textbf{2nd} prize on theme Light on the occasion International
Day of Light.
 \item \textbf{Won} the ’InQuizitive Minds’ Aptitude and Quiz competition in both the college round and city round;
and participated in the South India regional level, 2017
 \item Bagged \textbf{First} prize for Math Quiz and Programming skills intercollegiate competition, 2016.
 \item \textbf{Won} the ’CMRIT Hacks’, 2018 for building the mobile application - ’Teleport’
\end{itemize}

%	HOBBIES SECTION
%----------------------------------------------------------------------------------------

\section{Hobbies}
Play Table Tennis, solve Sudoku, minesweeper, puzzles, reading on Quora, teaching

\section{Strengths}
Quick Learner, Teaching, Punctual, Patience, Good Team-Worker and Analytical Skills.

\end{resume}
\end{document}
